SDR enhancement by clouds

### 2024-03-06 article/article.Rmd
Commit 2024-03-06 12:27

>>>>

## Clear Sky Irradiance

In order to set a threshold for the CE we had to create a "clear sky" radiation approximation.
For that reason, we decided to use the Libradtran model with monthly climatological data from AERONET, as our site is part of this network and operates a Cimel photometer since 2003.
We also use the Sun's total solar irradiance from NOAA and Earth - Sun distance calculated by Astropy.
We simulated radiation on multiple SZA's, for AOD at $500\,\text{nm}$ +/- 1 and 2 $\sigma$, for water column +/- 1 and 2 $\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer (afglms)" and "AFGL atmospheric constituent profile, midlatitude winter (afglmw)".
